---
title: "writing_functions"
author: "Xue Yang"
date: "10/25/2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

set.seed(1)

```


## Let's wirte some functions

Start small!!

```{r}
x = rnorm(25, 5, 3)

(x - mean(x)) / sd(x)
```

Write a function to compute a scores for a vector
```{r}
z_scores = function(x) {
  
  (x - mean(x)) / sd(x)
  
}
```

check to see if this works ...

```{r}
unif_sample = runif(100)

z_scores(x = unif_sample)
```

check some other examples ...
```{r}
# z_scores(3)
 
# z_scores("my name is jeff")

# z_scores(iris)

# z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

Put in some checks on inputs ...

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  (x - mean(x)) / sd(x)
}
```



### Mean and sd

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  mean_x =mean(x)
  sd_x = sd(x)
  
  c(mean_x, sd_x)
}

mean_and_sd(unif_sample)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  tibble(
    mean_x = mean(x),
    sd_x = sd(x)
  )
  
}

mean_and_sd(unif_sample)
```


## Multipke inputs

Look at simple linear regressions!

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```


Wirte a function that simulates data, fits and model, and returns the estimates. Inputs are sample size and true coefficients.

```{r}
sim_regression = function(n, beta0, beta1) {
  sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = beta0 + beta1 * x + rnorm(30, 0, 1)
  )
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
  beta0_hat = coef(ls_fit)[1],
  beta1_hat = coef(ls_fit)[2]
  )


}
```

```{r}
sim_regression(n = 3000, beta0 = 0, beta1 = -1)
```

```{r}
sim_regression(3000, 2, 5)
```


## Some old example

```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Wirte a function to extract reviews.

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

extract_reviews = function(url) {
  dynamite_html = read_html(url)
  
  review_titles = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  reviews
}

extract_reviews(url)
```

Let's extract a lot of reviews...

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  extract_reviews(urls[1]),
  extract_reviews(urls[2]),
  extract_reviews(urls[3]),
  extract_reviews(urls[4]),
  extract_reviews(urls[5])
)

dynamite_reviews
```


## example in tidy data

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = tolower(race)) %>% 
  select(movie, everything()) 

## there is some code repeat three times in "readxl::read_excel", then we need to write a function
```


```{r}
lotr_import = function(cell_range, movie_title) {
  
  readxl::read_excel("./data/LotR_Words.xlsx", range = cell_range) %>%
  mutate(movie = movie_title)
  
}

lotr_import("B3:D6", "fellowship_ring")
lotr_import("F3:H6", "two_towers")
lotr_import("J3:L6", "return_king")

```


## Scoping...

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)

## [1] 4
```

